\vspace{-1.5em} \bf A general and efficient representation of ancestral recombination graphs

### 2023-10-20 paper.tex
Change 2.7kb to 2.4kb
Because we now cut off the tail of the sequence, where there is no site information. This makes it easier to display default tsinfer outputs, which are trimmed to the first and last site.

\begin{figure} \begin{center}
\includegraphics[width=\textwidth]{illustrations/inference.pdf} \end{center}
\caption{\label{fig-inferred-args} Inference of an 11 sample ARG over a 2.7kb
region of the \textit{Drosophila melanogaster} ADH locus~\citep{kreitman1983nucleotide}.
Results for four different methods based on
(A) parsimony, (B) sampling the SMC$\prime$, (C) copying from
inferred ancestral haplotypes, and (D) correlated local tree estimation.
Edge colours are based on the time of the edge's child node
(lighter: older; darker: younger).
Position on the X and Y axes for the graph visualization is arbitrary.
Line width and node colour are as described in Fig.~\ref{fig-simplification}.
The graphic below each ARG shows the genomic intervals for each graph edge in the
corresponding ARGs: edges are horizontal lines, stacked in time order
(edges with youngest children at the bottom), with vertical dashed lines indicating
breakpoints between local trees.
}
\end{figure}

>>>>

\begin{figure} \begin{center}
\includegraphics[width=\textwidth]{illustrations/inference.pdf} \end{center}
\caption{\label{fig-inferred-args} Inference of an 11 sample ARG over a 2.4kb
region of the \textit{Drosophila melanogaster} ADH locus~\citep{kreitman1983nucleotide}.
Results for four different methods based on
(A) parsimony, (B) sampling the SMC$\prime$, (C) copying from
inferred ancestral haplotypes, and (D) correlated local tree estimation.
Edge colours are based on the time of the edge's child node
(lighter: older; darker: younger).
Position on the X and Y axes for the graph visualization is arbitrary.
Line width and node colour are as described in Fig.~\ref{fig-simplification}.
The graphic below each ARG shows the genomic intervals for each graph edge in the
corresponding ARGs: edges are horizontal lines, stacked in time order
(edges with youngest children at the bottom), with vertical dashed lines indicating
breakpoints between local trees.
}
\end{figure}
